Verifying Demonstrations

### 2018-08-28 paper/DB-anon-cred.tex
Bugfix: fixes indexing in DB-Schnorr protocol figure
Compacts DB-Schnorr figure slightly
Fixes typo in DB-Schnorr figure
Fixes erroneous bound for DF adversary in DB-Schnorr

\subsection{Reattempting a distance-bounding Schnorr protocol}

@@

We present the protocol in \cref{SchnorrFigure}.
The main difference to the original Schnorr protocol is that the prover commits 
to one random value but the verifier sends \emph{two challenges}.
This is also different from Brands-Chaum, where the prover and verifier jointly 
construct the challenge.
(We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.)
The verifier will request all \(|q|\) response-bits from one challenge and only 
\(l\) from the other.
The prover must know the responses for both challenges to successfully pass the 
\ac{DB} phase.

\begin{figure*}
  \centering
  \begin{tabular}{p{5cm}cp{5cm}}
    \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
    & &
    \(\DBSverify[g, q, A]\):
    \\
    \midrule

@@

    \midrule
    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < |q| + 
        l\)} \\

@@

    \(r_i\gets s_{b_i}[i]\)
    & \(\ProtoSendRight{r_i}\)
    & Record \(\Delta t_i\)
    \\

@@

    % null
    &
    & Construct \(r = s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
      b\).
    \\

    % null
    &
    & \(R \stackrel{?}{=} g^r A^{c_b}\)
    \\

@@

The \ac{DB} phase protects against distance fraud.
\Iac{DBDF} prover must wait for the challenge bit \(b_i\) before responding 
with \(r_i\).
The probability of successfully guessing the order of the challenge bits is 
\(2^{-(|q|+l)}\) per round or, in total, \(2^{-(|q|+l)n}\).

>>>>

\subsection{Reattempting a distance-bounding Schnorr protocol}%
\label{DBSchnorr}

@@

We present the protocol in \cref{SchnorrFigure}.
The main difference to the original Schnorr protocol is that the prover commits 
to one random value but the verifier sends \emph{two challenges}.
This is also different from Brands-Chaum, where the prover and verifier jointly 
construct the challenge.
(We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.)
The verifier will request all \(|q|\) response-bits from one challenge and only 
\(l > 0\) from the other.
The prover must know the responses for both challenges to successfully pass the 
\ac{DB} phase.

\begin{figure*}
  \centering
  \begin{tabular}{p{0.8\columnwidth}cp{0.8\columnwidth}}
    \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
    & &
    \(\DBSverify[g, q, A]\):
    \\
    \midrule

@@

    \midrule
    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < |q| + 
        l, j\gets 0\)} \\

@@

    \(r_i\gets s_{b_i}[jb_i + (i-j)(1-b_i)]\)
    & \(\ProtoSendRight{r_i}\)
    & Record \(\Delta t_i\)
    \\

    \(j \gets j + b_i\)
    &
    &
    \\

@@

    % null
    &
    & Construct \(r = s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
      b\).
      Accept if \(R = g^r A^{c_b}\).
    \\

@@

The \ac{DB} phase protects against distance fraud.
Once the prover has received \(l+1\) challenges set to \(b\), it knows that the 
remaining challenges must also be \(b\).
\Iac{DBDF} prover must thus wait for the challenge bit \(b_i\) before 
responding with \(r_i\) before at least \(l+1\) challenges.
Thus, the probability of successfully guessing the order of the challenge bits 
is \(2^{-(l+1)}\) per round in the worst case or, in total, \(2^{-(l+1)n}\).
